---
title: "Eating Out"
author: "Marbella"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(ech3wo = TRUE)
```

# Introduction 

In this write up we are analyzing if there is a difference in ethnicity in how frequently people eat out.

## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out.


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE, include=F}
GSS <-readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```


# Method
In order to interpret the data, Categorical Numerical method is needed to determine which ethnicity eats out more often.

## Desciptive Results 

### Grapghical results 


```{r}
barchartGC(~race + eatout, data=mydata)
barchartGC(~race + eatout, data=mydata, type="percent")
```


The bar chart suggests that there is a difference in the percentage of white ethnicity to other ethnicity in eating out. 

### Numerical Description   

```{r}
table1 <- xtabs(~race + eatout, data=mydata) 
rowPerc(table1)
colPerc(table1)
```
The results in this numerical description shows the frequency of eating out in 
white ethnicity as opposed to block and other ethnicity. Showing white ethnicity frequency of eating out is more than block and other ethnicity. 


## inferitial results
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisherXY(mydata$race,mydata$eatout,printAll=T)
```


The P value number is so small that I fail to reject the null hypothesis. There is a difference in eating out with whites and blacks. Whites eat out more than blacks. No differences in other ethnicity . The answer being that whites eat out more. 
Chi squared test shows the p value 0.0008179, we see the number is so small that we reject the null hypothesis. 
The fisher exact test for count data shows that the p value 0.001208 is also very small that we reject the null hypothesis.


## Discussion and Conclusion

I conclude there is difference in ethnicity eating out. I fail to reject the Null hypothesis. There is a difference in white eating out more than black according to the p-value = 0.0003864. , but there is no difference of white eating more than other ethnicity. The p-value = 0.3543. There is also no difference in black eating more than other ethnicity according to the p-value = 0.2815. Therefore, I reject the Null hyposthesis.  

